---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PPGISr
Welcome to PPGISr, an R package for Public participatory GIS (PPGIS).


### Run an example map
PPGISr comes with a sample map that loads as default. The example map provides an area of Minnesota and three land cover categories to choose from. 

```{r basic, eval=FALSE}
PPGISr::run_app()
```

### Create your own categorise 
You can also suggest which categories of land cover you would like to map.

```{r categories, eval=FALSE}
PPGISr::run_app(mapping_categories = c("Trees", 
                                       "Flowers",
                                       "Water"))
```

## Issues and bugs

This package requires an internet connection as well as a connection to
the Flickr API, which may not be constantly available.

If you discover a bug that is not already a [reported issue](https://github.com/GLISA-umich/PPGISr/issues), please [open a new issue](https://github.com/GLISA-umich/PPGISr/issues/new) providing a reproducible example.

