---
title: "PPGISr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PPGISr}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
runtime: shiny
---

```{r, include = FALSE}
 knitr::opts_chunk$set(
   collapse = TRUE,
   comment = "#>"
 )
```

Welcome to PPGISr, an R package for Public participatory GIS (PPGIS).

### Install PPGISr
```{r eval=FALSE}
library(devtools)
install_github("https://github.com/GLISA-umich/PPGISr")
```

### Run an example map
PPGISr comes with a sample map that loads as default. The example map provides an area of Minnesota and three land cover categories to choose from. 

```{r basic, eval=FALSE}
PPGISr::run_app()
```

### Create your own categorise 
You can also suggest which categories you would like to map (e.g. land use, environmental and social vulnerabilities).

```{r categories, eval=FALSE}
PPGISr::run_app(mapping_categories = c("Trees", 
                                       "Flowers",
                                       "Water"))
```

### Create your own colors
It is also possible to add colors that corresponds to these categories

```{r, eval=F, echo=T}
## This must be a vector of the same length as the mapping categories
run_app(mapping_categories = c("flowers", "lake", "trees"),
        mapping_colors = c("green", "red", "blue"))
```

### Add your own editable map
Users can specify the editable map layer, allowing for different locations and regular geographic units with a desire resolution (e.g. census tract, regular tessellation) for decision-making
```{r, eval=F, echo=T}
## We recommend using the sf library to load spatial vector data
library(sf)
## Spatial data should use World Geodetic System 1984 (WGS84) coordinate reference system(crs)
editable_map <- st_read(system.file("shape/nc.shp", package="sf"))

run_app(editable_map = editable_map, base_map = NULL)
