---
title: "PPGISr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PPGISr}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
runtime: shiny
---

```{r, include = FALSE}
 knitr::opts_chunk$set(
   collapse = TRUE,
   comment = "#>"
 )
```

PPGISr is a shiny app for collecting spatially explicit data from users
```{r setup}
library(PPGISr)
```

The `run_app()` function initializes the app with default data 
```{r include = FALSE}
run_app()
```

You can customize your PPGISr interface by adding mapping categories
```{r eval=F}
run_app(mapping_categories = c("flowers", "lake", "trees"))
```

It is also possible to add colors that coorispond to these categories

```{r, eval=F, echo=T}
## This must be a vector of the same length as the mapping categories
run_app(mapping_categories = c("flowers", "lake", "trees"),
        mapping_colors = c("green", "red", "blue"))
```

Users can also specify the editable map layer, allowing for different location and resoultion of decision units
```{r, eval=F, echo=T}
## We recommend using the sf library to load spatial vector data
library(sf)
## Spatial data should use World Geodetic System 1984 (WGS84) coordinate reference system(crs)
editable_map <- st_read(system.file("shape/nc.shp", package="sf"))

run_app(editable_map = editable_map, base_map = NULL)
```
